Addition and removal energies of circular quantum dots

### 2017-09-05 Manuscript/paper.tex
Add more bibliographic references

In this paper, we analyze the application of several methods to the quantum dot systems, including the Hartree--Fock (HF) method \cite{hartree_1928,Fock1930}, M\o ller--Plesset perturbation theory (MP) \cite{1934PhRv...46..618M}, the in-medium similarity renormalization group (IM-SRG) method \cite{IMSRG}, coupled cluster (CC) theory \cite{PhysRevB.67.045320,heidari:114708,PhysRevB.84.115302}, quasidegenerate perturbation theory (QDPT) \cite{0022-3700-7-18-010,Kvasnicka1974}, and equations-of-motion (EOM) methods \cite{RevModPhys.40.153}.  We compare them against variational and diffusion Monte Carlo (VMC and DMC) \cite{PhysRevB.68.035304,PhysRevB.62.8120,PhysRevB.84.115302,PhysRevB.54.4780} and full configuration interaction (FCI) theory \cite{olsen2013thesis,JJAP.36.3924,PhysRevB.56.6428,2008arXiv0810.2644K,rontani:124102} results, where available, from existing literature.

@@

@@

To analyze the rate of convergence more quantitatively, we define $\rho_K$ as the relative backward difference of the energy (\textit{relative slope}):
\begin{align*}
  \rho_K = \frac{\varepsilon_K - \varepsilon_{(K - 1)}}{\varepsilon_K}.
\end{align*}
The denominator allows the quantity to be meaningfully compared between different systems.  We expect this quantity to become increasingly small as the calculations converge.

@@

As derived by Kvaal \cite{PhysRevB.80.045321,Kvaal2007}, the asymptotic convergence of the quantum dot observables in a finite harmonic oscillator basis can be approximately described by a power law model:
\begin{align*}
  \Delta E \propto K^{-\beta},
\end{align*}
where $\Delta E$ is the difference between the finite-basis result and the infinite-basis result, $K$ is the number of shells in the single-particle basis, and $\beta$ is some positive real exponent.  The \textit{smoothness} of the exact wave function determines the rate of the convergence: the more times the exact wave function can be differentiated, the higher the exponent $\beta$.

>>>>

In this paper, we analyze the application of several methods to the quantum dot systems, including the Hartree--Fock (HF) method \cite{hartree_1928,Fock1930}, M\o ller--Plesset perturbation theory (MP) \cite{1934PhRv...46..618M}, the in-medium similarity renormalization group (IM-SRG) method \cite{IMSRG}, coupled cluster (CC) theory \cite{PhysRevB.67.045320,heidari:114708,PhysRevB.84.115302}, quasidegenerate perturbation theory (QDPT) \cite{0022-3700-7-18-010,Kvasnicka1974}, and equations-of-motion (EOM) methods \cite{RevModPhys.40.153,StantonBartlettEOM,EMRICH1981379}.  We compare them against variational and diffusion Monte Carlo (VMC and DMC) \cite{PhysRevB.68.035304,PhysRevB.62.8120,PhysRevB.84.115302,PhysRevB.54.4780} and full configuration interaction (FCI) theory \cite{olsen2013thesis,JJAP.36.3924,PhysRevB.56.6428,2008arXiv0810.2644K,rontani:124102} results, where available, from existing literature.

@@

Lastly, we note that from the above discussion it is clear that the IMSRG is closely related to several other well-known methods of quantum chemistry such as coupled cluster theory \cite{shavitt2009many}, canonical transformation theory \cite{White:cond-mat0201346,CTreview}, the irreducible (or anti-Hermitian) contracted Schr\"odinger equation approach \cite{Mazzioti1,Mazzioti2}, and the driven similarity renormalization group method \cite{Evangelista}.  We refer the reader to Ref.\ \cite{HeikoReview} for a discussion of the similarities and differences from these approaches.

@@

To analyze the rate of convergence more quantitatively, we define $\rho_K$ as the relative backward difference of the energy (\textit{relative slope}):
\begin{align*}
  \rho_K = \frac{\varepsilon_K - \varepsilon_{(K - 1)}}{\varepsilon_K}.
\end{align*}
The denominator allows the quantity to be meaningfully compared between different systems.  We expect this quantity to become increasingly small as the calculations converge towards the complete basis set limit.

@@

To minimize basis set truncation errors, one can either use explicitly correlated R12/F12 methods that account for the correct cusp behavior in many-electron wave functions\cite{Kutzelnigg1985,KLOPPER198717,explicitcorrelationreview}, or one can use basis extrapolation techniques. In the present work, we focus on the latter. As derived by Kvaal \cite{PhysRevB.80.045321,Kvaal2007}, the asymptotic convergence of the quantum dot observables in a finite harmonic oscillator basis can be approximately described by a power law model:
\begin{align*}
  \Delta E \propto K^{-\beta},
\end{align*}
where $\Delta E$ is the difference between the finite-basis result and the infinite-basis result, $K$ is the number of shells in the single-particle basis, and $\beta$ is some positive real exponent.  The \textit{smoothness} of the exact wave function determines the rate of the convergence: the more times the exact wave function can be differentiated, the higher the exponent $\beta$.
